\textit{Supplementary materials for:} The psychological arrow of time drives temporal asymmetries in inferring unobserved past and future events

### 2023-09-23 paper/supplement.tex
finished a complete round of edits (main text + supplement)

\begin{table}[]
\caption{\textbf{Stimuli description.}}
\begin{center}
\resizebox{\textwidth}{!}{
\begin{threeparttable}
\begin{tabular}{rrrrlll}
\toprule
\multirow{2}{*}{Storyline} &
  \multirow{2}{*}{Segment} &
  \multirow{2}{*}{Episode} &
  \multirow{2}{*}{Duration (s)} &
  \multirow{2}{*}{Main characters} &
  \multicolumn{2}{l}{Number of events\tnote{a}} \\ \cmidrule(l){6-7} 
  &    &   &     &                                & Onscreen      & Offscreen\tnote{b} \\ \midrule
1 & 1  & 1 & 105 & Beth, Sheila, Rob, Leo         & 4             & 7         \\
1 & 2  & 1 & 172 & Beth, Sheila, Rob, Leo         & 7 {[}1{]}     & 3         \\
1 & 3  & 1 & 70  & Beth, Sheila, One neighbor     & 6             & 2         \\
1 & 4  & 1 & 135 & Beth, Sheila                   & 8 {[}1{]}     & 1         \\
1 & 5  & 1 & 90  & Beth, Rob, April               & 8             & 4         \\
1 & 6  & 1 & 188 & Beth, Rob                      & 6 {[}2{]}     & 1         \\
1 & 7  & 1 & 91  & Beth, Sheila                   & 5 {[}1{]}     & 2         \\
1 & 8  & 1 & 142 & Beth, April                    & 4 (1) {[}2{]} & 3 (1)     \\
1 & 9  & 2 & 134 & Beth, April                    & 4 {[}2{]}     & 1         \\
1 & 10 & 2 & 58  & Beth                           & 3 {[}1{]}     & 6 {[}1{]} \\
1 & 11 & 2 & 159 & Beth, Rob                      & 9             &           \\
2 & 1  & 1 & 70  & Simone, Karl                   & 3 {[}1{]}     & 6         \\
2 & 2  & 1 & 119 & Simone, Karl, Naomi, Tommy     & 4 {[}1{]}     & 2         \\
2 & 3  & 1 & 58  & Simone, Karl, Tommy            & 4             & 2         \\
2 & 4  & 1 & 102 & Simone, Karl                   & 4             & 6         \\
2 & 5  & 1 & 134 & Simone, Karl, Tommy            & 6 (3) {[}1{]} & 3         \\
2 & 6  & 1 & 81  & Simone, Karl, Neighbors, Wanda & 4 (1)         & 6         \\
2 & 7  & 1 & 194 & Simone, Tommy                  & 8             & 3         \\
2 & 8  & 2 & 101 & Simone, Karl                   & 3 (1)         & 1         \\
2 & 9  & 2 & 86  & Simone, Tommy                  & 4 {[}1{]}     & 3         \\
2 & 10 & 2 & 232 & Simone, Karl                   & 6 {[}1{]}     & 3         \\
2 & 11 & 2 & 189 & Simone, Naomi, Tommy           & 7 (1) {[}1{]} &           \\ \bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] Number of partial events (see methods) shown in parentheses; number of summary events shown in square brackets.
\item[b] Offscreen events happened between the current segment and the next segment.
\end{tablenotes}
\end{threeparttable}
}
\end{center}
\end{table}

\begin{table}
    \footnotesize
    \caption{List of datasets analyzed in our meta-analysis (see Fig. 8).}
    \label{tab:datasets}
    \begin{tabular}{p{0.6in}|l|p{2in}|l|p{0.5in}|p{0.5in}|p{0.5in}}
        \toprule
        \textbf{Dataset} & \textbf{Short name} & \textbf{Description} & \textbf{Category} & \textbf{Number of observations} & \textbf{Ob\-ser\-va\-tion type} & \textbf{Number of words} \\
        \midrule
        Internet Movie Script Database & IMSDb & A collection of transcripts from roughly 1000 popular movies. & Film & 1091 & Transcript & 26023348 \\
        \midrule
        Movie Dialogues Dataset & Movies & A large collection of fictional conversations extracted from raw movie scripts. & Film & 304713 & Utterance & 3209921 \\
        \midrule
        Switchboard Dialog Act Corpus & Switchboard & A collection of five-minute telephone conversations between two participants, annotated with speech act tags. & Speech & 122646 & Utterance & 2052779 \\
        \midrule
        Supreme Court Corpus & SCOTUS & A collection of cases from the U.S. Supreme Court, along with transcripts of oral arguments. & Speech & 1700789 & Utterance & 71889094 \\
        \midrule
        Tennis Interviews & Tennis & Transcripts for tennis singles post-match press conferences for major tournaments between 2007 to 2015. & Speech & 163948 & Utterance & 7043118 \\
        \midrule
        Persuasion for Good Corpus & PfG & A collection of online conversations generated by Amazon Mechanical Turk workers, where one participant (the persuader) tries to convince the other (the persuadee) to donate to a charity. & Speech & 20932 & Utterance & 351759 \\
        \midrule
        Intelligence Squared Debates Corpus & IQ2 & This dataset contains transcripts of debates held as part of Intelligence Squared Debates. & Speech & 26562 & Utterance & 1898509 \\
        \midrule
        Group Affect and Performance Corpus & GAP & Group members completed a Winter Survival Task (WST), a group decision-making exercise where participants must rank 15 items according to their importance in a hypothetical plane crash scenario. Participants first rank the items individually. Then, each group was given a maximum of 15 minutes to complete the WST. The group’s conversations and deliberations during this task were recorded as conversations in this dataset. & Speech & 8009 & Utterance & 45989 \\
        \midrule
        The Chair & Chair & Scraped transcripts from The Chair, Season 1. & Television & 6 & Transcript & 19197 \\
        \midrule
        Friends Corpus & Friends & A collection of all the conversations that occurred over 10 seasons of Friends, a popular American TV sitcom that ran in the 1990s. & Television & 67373 & Utterance & 622894 \\
        \midrule
        Gutenberg Dialogue Dataset & Gutenberg & Dialogues extracted from the Project Gutenberg collection. & Text & 14773741 & Utterance & 327519461 \\
        \midrule
        Reddit Corpus & Reddit & A collection of Corpuses of Reddit data built from Pushshift.io Reddit Corpus. Each Corpus contains posts and comments from an individual subreddit from its inception until Oct 2018. & Text & 74468 & Utterance & 3080662 \\
        \bottomrule
    \end{tabular}
\end{table}

@@

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{supp1.pdf}
    \caption{\textbf{Mean proportion of target events hit (A), precision (B), and convergence (C) as a function of number of segments watched in each storyline, in participants' uncued and character-cued retrodictions and predictions.} Grey lines represent the least squares fits.}
    \label{fig:supp1}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{supp2.pdf}
    \caption{\textbf{Mean number of events hit for each event type, in participants' uncued and character-cued retrodictions and predictions, averaged across just-watched segments.}}
    \label{fig:supp2}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{supp3.pdf}
    \caption{\textbf{(A)} References in each storyline. \textbf{(B)} Distribution of reference lags.}
    \label{fig:supp3}
\end{figure}

>>>>

\begin{table}[]
\caption{\textbf{Stimulus descriptions (main experiment).}}
\begin{center}
\resizebox{\textwidth}{!}{
\begin{threeparttable}
\begin{tabular}{rrrrlll}
\toprule
\multirow{2}{*}{Storyline} &
  \multirow{2}{*}{Segment} &
  \multirow{2}{*}{Episode} &
  \multirow{2}{*}{Duration (s)} &
  \multirow{2}{*}{Main characters} &
  \multicolumn{2}{l}{Number of events\tnote{a}} \\ \cmidrule(l){6-7} 
  &    &   &     &                                & Onscreen      & Offscreen\tnote{b} \\ \midrule
1 & 1  & 1 & 105 & Beth, Sheila, Rob, Leo         & 4             & 7         \\
1 & 2  & 1 & 172 & Beth, Sheila, Rob, Leo         & 7 {[}1{]}     & 3         \\
1 & 3  & 1 & 70  & Beth, Sheila, One neighbor     & 6             & 2         \\
1 & 4  & 1 & 135 & Beth, Sheila                   & 8 {[}1{]}     & 1         \\
1 & 5  & 1 & 90  & Beth, Rob, April               & 8             & 4         \\
1 & 6  & 1 & 188 & Beth, Rob                      & 6 {[}2{]}     & 1         \\
1 & 7  & 1 & 91  & Beth, Sheila                   & 5 {[}1{]}     & 2         \\
1 & 8  & 1 & 142 & Beth, April                    & 4 (1) {[}2{]} & 3 (1)     \\
1 & 9  & 2 & 134 & Beth, April                    & 4 {[}2{]}     & 1         \\
1 & 10 & 2 & 58  & Beth                           & 3 {[}1{]}     & 6 {[}1{]} \\
1 & 11 & 2 & 159 & Beth, Rob                      & 9             &           \\
2 & 1  & 1 & 70  & Simone, Karl                   & 3 {[}1{]}     & 6         \\
2 & 2  & 1 & 119 & Simone, Karl, Naomi, Tommy     & 4 {[}1{]}     & 2         \\
2 & 3  & 1 & 58  & Simone, Karl, Tommy            & 4             & 2         \\
2 & 4  & 1 & 102 & Simone, Karl                   & 4             & 6         \\
2 & 5  & 1 & 134 & Simone, Karl, Tommy            & 6 (3) {[}1{]} & 3         \\
2 & 6  & 1 & 81  & Simone, Karl, Neighbors, Wanda & 4 (1)         & 6         \\
2 & 7  & 1 & 194 & Simone, Tommy                  & 8             & 3         \\
2 & 8  & 2 & 101 & Simone, Karl                   & 3 (1)         & 1         \\
2 & 9  & 2 & 86  & Simone, Tommy                  & 4 {[}1{]}     & 3         \\
2 & 10 & 2 & 232 & Simone, Karl                   & 6 {[}1{]}     & 3         \\
2 & 11 & 2 & 189 & Simone, Naomi, Tommy           & 7 (1) {[}1{]} &           \\ \bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] Number of partial events (see methods) shown in parentheses; number of summary events shown in square brackets.
\item[b] Offscreen events happened between the current segment and the next segment.
\end{tablenotes}
\end{threeparttable}
}
\end{center}
\end{table}

\begin{table}
    \footnotesize
    \caption{List of datasets analyzed in our meta-analysis (see Fig. 8).}
    \label{tab:datasets}
    \begin{tabular}{p{0.6in}|l|p{2.2in}|l|p{0.5in}|p{0.5in}|p{0.5in}}
        \toprule
        \textbf{Dataset} & \textbf{Short name} & \textbf{Description} & \textbf{Category} & \textbf{Number of observations} & \textbf{Ob\-ser\-va\-tion type} & \textbf{Number of words} \\
        \midrule
        Internet Movie Script Database & IMSDb & A collection of transcripts from roughly 1000 popular movies. & Film & 1091 & Transcript & 26023348 \\
        \midrule
        Movie Dialogues Dataset & Movies & A large collection of fictional conversations extracted from raw movie scripts. & Film & 304713 & Utterance & 3209921 \\
        \midrule
        Switchboard Dialog Act Corpus & Switchboard & A collection of five-minute telephone conversations between two participants, annotated with speech act tags. & Speech & 122646 & Utterance & 2052779 \\
        \midrule
        Supreme Court Corpus & SCOTUS & A collection of cases from the U.S. Supreme Court, along with transcripts of oral arguments. & Speech & 1700789 & Utterance & 71889094 \\
        \midrule
        Tennis Interviews & Tennis & Transcripts for tennis singles post-match press conferences for major tournaments between 2007 to 2015. & Speech & 163948 & Utterance & 7043118 \\
        \midrule
        Persuasion for Good Corpus & PfG & A collection of online conversations generated by Amazon Mechanical Turk workers, where one participant (the persuader) tries to convince the other (the persuadee) to donate to a charity. & Speech & 20932 & Utterance & 351759 \\
        \midrule
        Intelligence Squared Debates Corpus & IQ2 & This dataset contains transcripts of debates held as part of Intelligence Squared Debates. & Speech & 26562 & Utterance & 1898509 \\
        \midrule
        Group Affect and Performance Corpus & GAP & Group members completed a Winter Survival Task (WST), a group decision-making exercise where participants must rank 15 items according to their importance in a hypothetical plane crash scenario. Participants first rank the items individually. Then, each group was given a maximum of 15 minutes to complete the WST. The group’s conversations and deliberations during this task were recorded as conversations in this dataset. & Speech & 8009 & Utterance & 45989 \\
        \midrule
        The Chair & Chair & Scraped transcripts from The Chair, Season 1. & Television & 6 & Transcript & 19197 \\
        \midrule
        Friends Corpus & Friends & A collection of all the conversations that occurred over 10 seasons of Friends, a popular American TV sitcom that ran in the 1990s. & Television & 67373 & Utterance & 622894 \\
        \midrule
        Gutenberg Dialogue Dataset & Gutenberg & Dialogues extracted from the Project Gutenberg collection. & Text & 14773741 & Utterance & 327519461 \\
        \midrule
        Reddit Corpus & Reddit & A collection of Corpuses of Reddit data built from Pushshift.io Reddit Corpus. Each Corpus contains posts and comments from an individual subreddit from its inception until Oct 2018. & Text & 74468 & Utterance & 3080662 \\
        \bottomrule
    \end{tabular}
\end{table}

@@

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{supp1.pdf}
    \caption{\textbf{Mean proportion of target events hit (A), precision (B), and convergence (C) as a function of number of segments watched in each storyline, in the main experiment participants' uncued and character-cued retrodictions and predictions.} Grey lines represent the least squares fits.}
    \label{fig:supp1}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{supp2.pdf}
    \caption{\textbf{Mean number of events hit for each event type, in the main experiment participants' uncued and character-cued retrodictions and predictions, averaged across just-watched segments.}}
    \label{fig:supp2}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{supp3.pdf}
    \caption{\textbf{(A)} References in each storyline in the main experiment stimulus. \textbf{(B)} Distribution of reference lags in the main experiment stimulus.}
    \label{fig:supp3}
\end{figure}
